Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-02-11 ltx/data_paper/DataPaper.tex
edits to maximization

In order to find the maximum of the $\mathcal{Q}$-function Differntiating with respect to $\boldsymbol\theta$ we have
\begin{equation}\label{eq:Qpartialtheta}
 \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=2\Xi_0-\boldsymbol\theta^\top(\Xi_2^\top+\Xi_2)-2\xi\Xi_3
\end{equation}
noting that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
\begin{equation}\label{eq:theta}
 \boldsymbol \theta=\Xi_2^{-1}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
\end{equation}
similarly differentiating with respect to $\xi$ we have
\begin{equation}\label{eq:Qpartialxi}
 \frac{\partial \mathcal Q}{\partial \xi}=2tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace -2 \Xi_3 \boldsymbol\theta - 2\xi tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace
\end{equation}
substituting \ref{eq:theta} in \ref{eq:Qpartialxi} and equating to zero we get
\begin{equation}
 \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_3^\top}
\end{equation}
Rewrite equation~\ref{eq:Voldermont} as
\begin{equation}
 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')\propto-(T-1)n_y\ln\sigma^2_{\epsilon}-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
\end{equation}
differentiating with respect to $\sigma_{\epsilon}^2$
\begin{equation}
  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon^4}}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
\end{equation}
setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
\begin{equation}
 \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
\end{equation}

>>>>

Consider first the maximization of $\mathcal{Q}$-function with respect to $\boldsymbol\theta$, we can write
\begin{equation}\label{eq:Qpartialtheta}
 \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=\frac{2}{\sigma_d^2}\Xi_2-\frac{1}{\sigma_d^2}\boldsymbol\theta^\top(\Xi_3^\top+\Xi_3)-\frac{2\xi}{\sigma_d^2}\Xi_4
\end{equation}
noting that $\Xi_3$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
\begin{equation}\label{eq:theta}
 \boldsymbol \theta=\Xi_3^{-1}\left(\Xi_2^\top-\xi\Xi_4^\top \right).
\end{equation}
The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function.
Now maximizing with respect to $\sigma_{\epsilon}^2$ we get
\begin{equation}
  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
\end{equation}
setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
\begin{equation}
 \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
\end{equation}
A second derivative test shows that this is indeed the maximum.
